Predictors of frog survival following translocations - primary analyses

### 2023-03-23 code/translocation_survival_analysis.Rmd
Update file path for sourced script
Revert "Update file path for sourced script"
This reverts commit 03a94dfefffa460c0f93a3dd46880bf9252ab56a.
Update ggplot code to replace deprecated aesthetic

source("classification_summary.R")
```

@@

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>%
  ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order)
      geom_linerange(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.5, position = position_dodge2(width=0.5)) +
      geom_point(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor), size = 3, position = position_dodge2(width=0.5)) + 
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", size = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

@@

#### Load packages

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)

source("classification_summary.R")
```

#### Create frog translocation dataset for analysis

@@

# use untransformed predictor (elevation) to make plot easier to interpret  
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv)) +  #   "ggplot(aes(x = (elev_z * 2*sd_elev) + mean_elev, y = surv)) +" gives identical result
          geom_line(aes(y = .epred, group = .draw), color = "blue", size = 0.2, alpha = 1) +
        # geom_point(aes(y = .epred)) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival")

@@

p_elev <- d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = elevation)) + 
          geom_ribbon(aes(ymin = lower, ymax = upper), fill= "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", size = 1, alpha = 1) +
          labs(x = "Elevation of recipient site (meters)", y = "P(1-year frog survival)") +
          annotate(geom = "text", x = 2500, y = 0.94, label = "B", size = 4) +
          theme_classic()

@@

p_snowt1 <- d1_snowt1z %>% 
  select(site_id, translocation_id, snowt1_z, snow_t1, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(snow_t1) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = snow_t1)) +
          geom_ribbon(aes(ymin = lower, ymax = upper), fill = "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", size = 1, alpha = 1) +
          labs(x = "Winter severity in year t+1\n(% of average snow depth)", y = "P(1-year frog survival)") +
          annotate(geom = "text", x = 157, y = 0.92, label = "A", size = 4) +
          theme_classic()

@@

# plot individual draws grouped by sex 
pal <- c("#0d0887", "#f89540")
d1_elevz_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv, color = sex)) +
          geom_line(aes(y = .epred, group = paste(sex, .draw)), size = 0.4, alpha = 0.5) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival") +
          scale_color_manual(values = pal) + 
          theme_classic()

# plot medians and uncertainty ribbons grouped by sex
p_elevsex <- d1_elevz_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation, sex) %>% 
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = elevation, group = sex)) +
          geom_ribbon(aes(ymin = lower, ymax = upper, fill = sex), alpha = 0.2, linetype = 0) +
          geom_line(aes(y = median, color = sex), size = 1, alpha = 1) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival") +
          scale_color_manual(values = pal) + 
          scale_fill_manual(values = pal) +
          theme_classic()

>>>>

source("code/classification_summary.R")
```

@@

cohort_survival_plot <- cohort_survival %>% 
  mutate(release_year = year(release_date)) %>% 
  group_by(site_id) %>% 
  summarize(plot_survival = mean(median_survival)) %>%  # create variable by which to order sites for plotting
  arrange(plot_survival) %>% 
  mutate(siteid_order = row_number()) %>% 
  inner_join(cohort_survival, by = "site_id") %>% 
  inner_join(donors, by = "site_id") %>% 
  select(-plot_survival) %>%
  ggplot(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor)) +  # reorder site_id by siteid_order)
      geom_linerange(aes(ymin = lo_survival, ymax = hi_survival), color = "black", width = 0.5, position = position_dodge2(width=0.5)) +
      geom_point(aes(x = reorder(site_id, siteid_order), y = median_survival, color = donor), size = 3, position = position_dodge2(width=0.5)) + 
      scale_color_manual(values = palette1) + 
      labs(x = "Recipient site", y = "1-year frog survival") +
      theme_classic() +
      theme(
        legend.background = element_rect(color = "black", linewidth = 0.3),
        legend.position = c(0.2, 0.8),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))

@@

#### Frog translocation dataset for analysis

@@

# use untransformed predictor (elevation) to make plot easier to interpret  
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv)) +  #   "ggplot(aes(x = (elev_z * 2*sd_elev) + mean_elev, y = surv)) +" gives identical result
          geom_line(aes(y = .epred, group = .draw), color = "blue", linewidth = 0.2, alpha = 1) +
        # geom_point(aes(y = .epred)) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival")

@@

p_elev <- d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = elevation)) + 
          geom_ribbon(aes(ymin = lower, ymax = upper), fill= "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          labs(x = "Elevation of recipient site (meters)", y = "P(1-year frog survival)") +
          annotate(geom = "text", x = 2500, y = 0.94, label = "B", size = 4) +
          theme_classic()

@@

p_snowt1 <- d1_snowt1z %>% 
  select(site_id, translocation_id, snowt1_z, snow_t1, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(snow_t1) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = snow_t1)) +
          geom_ribbon(aes(ymin = lower, ymax = upper), fill = "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          labs(x = "Winter severity in year t+1\n(% of average snow depth)", y = "P(1-year frog survival)") +
          annotate(geom = "text", x = 157, y = 0.92, label = "A", size = 4) +
          theme_classic()

@@

# plot individual draws grouped by sex 
pal <- c("#0d0887", "#f89540")
d1_elevz_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv, color = sex)) +
          geom_line(aes(y = .epred, group = paste(sex, .draw)), linewidth = 0.4, alpha = 0.5) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival") +
          scale_color_manual(values = pal) + 
          theme_classic()

# plot medians and uncertainty ribbons grouped by sex
p_elevsex <- d1_elevz_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation, sex) %>% 
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = elevation, group = sex)) +
          geom_ribbon(aes(ymin = lower, ymax = upper, fill = sex), alpha = 0.2, linetype = 0) +
          geom_line(aes(y = median, color = sex), linewidth = 1, alpha = 1) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival") +
          scale_color_manual(values = pal) + 
          scale_fill_manual(values = pal) +
          theme_classic()
